---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# webwork: An R package for WeBWorK

[![Travis-CI Build Status](https://travis-ci.org/rpruim/webwork.svg?branch=master)](https://travis-ci.org/rpruim/webwork)

## Installation

You can install webwork from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("rpruim/webwork")
```

## Current functionality
 
 * `crypt()` -- hashes passwords as per WeBWorK requirements (require `perl` currently)
 
 * `ww_roster()` -- generates a roster data frame that can be saved to to a CSV file (but named `.lst`) and uploaded to WeBWorK.  Uses `crypt()` for the necessary password hashing.
 
 * `ww_read_gradebook()` -- a simple gradebook ingestor that process the 7 header lines of the files WeBWorK exports and returns a sane data frame for post processing.
The goal of webwork is to ...

